Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-01-07 paper/abstract.tex
Move imp to figs and move figs to proof section
Restructure sections and file names
Change title and abstract

\begin{abstract}
The Keccak function in the SHA-3 NIST standard is responsible for the major computations of all SHA-3 hashes and Shake functions.
These functions are a key piece in modern secure hash functions. 
This work extends and improves on the methodology used in the verification of Amazon’s s2n HMAC and OpenSSL’s SHA2-256 inner hash function. 
It uses the Software Analysis Workbench (SAW) to prove out functional equivalence between OpenSSL’s SHA-3 Keccak function and a verified implementation of SHA-3 in the domain-specific language Cryptol. 
SAW creates contracts (called overrides), a functions input to output relationship, which allows for a modular approach to writing proofs. 
This work leverages SAW by creating overrides to block out computation and creating a compositional proof that remains within the capacity of an SMT solver. 
This work amends Cryptol through utility functions to handle looping which greatly simplifies the visual inspection the Cryptol implementation to provide strong assurance of correctness. 
The results of this work indicate that this methodology works with modern cryptographic specifications and that a modular approach in cryptographic algorithm design greatly simplifies the verification process.
\end{abstract}

>>>>

\shaThree\ is the new standard from \nist\ for computing digests. 
\openssl\ is one of the most widely used implementations of cryptographic protocols.
\cryptol\ and the Software Analysis Workbench (\saw) are a language and verification engine to specify cryptographic primitives and prove equivalence to implementations.
As digests are the basis for all cryptographic protocols, the research in this paper is an automated \saw\ proof of equivalence between the \shaThree\ standard and the actual \openssl\ implementation in C.
The research contributes \cryptol\ specifications for the published standard and the \openssl\ implementation of the standard with its several changes.
The equivalence proof shows the importance of overrides in \saw\ to replace C code with \cryptol\ to reduce the complexity of the proof obligations that must be accomplished relative to the implementation in C.
The research establishes the viability of verifying modern cryptographic primitives and the importance of modularity in their definitions, and implementations, for overrides.

% The \keccak\ function in the SHA-3 NIST standard is responsible for the major computations of all SHA-3 hash constructs.
% These constructs form the basis for modern secure hashing.
% This work extends and improves the methodology used to verify Amazon's s2n HMAC and OpenSSL's SHA2-256 inner hash function. 
% It uses the Software Analysis Workbench (SAW) to prove out functional equivalence between OpenSSL's SHA-3 Keccak function and a verified implementation of SHA-3 in Cryptol, a domain-specific language for cryptography. 
% SAW allows for a modular approach to writing proofs through the use of contracts, which define a functions input to output relationship.
% Each contract, also called an override, is an obligation in the full proof.
% This work leverages SAW by creating overrides to decompose computation and create a compositional proof that is within the capacity of an SMT solver. 
% Visual inspection between Cryptol and the NIST standard is simplified through the creation of Cryptol utility functions.
% These utility functions wrap the complex list comprehensions required for looping in Cryptol.
% The results of this work indicates that a modular approach in cryptographic algorithm design greatly simplifies the verification process, as exemplified by SHA-3.

### 2022-01-07 paper/paper.tex
Revise the overview of saw
Revise OpenSSL
Fix Brett's name
Change title and abstract

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand{\UrlFont}{\color{blue}\rmfamily}
\newcommand{\keccak}{\textsc{Keccak}}
\newcommand{\shaThree}{\texttt{SHA-3}}
\newcommand{\nist}{\texttt{NIST}}
\newcommand{\fips}{\texttt{FIPS 202}}
\newcommand{\saw}{\texttt{SAW}}
\newcommand{\cryptol}{Cryptol}
\newcommand{\openssl}{OpenSSL}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\algoref}[1]{Alg.~\ref{#1}}
\newcommand{\lineref}[1]{Line~\ref{#1}}
\newcommand{\secref}[1]{Sec.~\ref{#1}}

\begin{document}
%
\title{Verification of OpenSSL's SHA3 \keccak\ function using the Software Analysis Workbench}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
  Parker Hanson\inst{1} \and
  Benjamin Winters\inst{1} \and
  Eric Mercer\inst{1}\orcidID{0000-0002-2264-2958} \and
  Bret Decker\inst{1}
}
%
\authorrunning{P. Hanson et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
  Brigham Young University, Provo UT 84602, USA
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{abstract}
\keywords{verification \and cryptography \and symbolic execution \and SHA3.}
\end{abstract}

@@

\section{FIPS 202 Specification in \cryptol}\label{sec:fips}
\input{fips202}

\section{\shaThree\ from \openssl\ in \cryptol}\label{sec:openssl}
\input{openssl}

>>>>

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand{\UrlFont}{\color{blue}\rmfamily}
\newcommand{\keccak}{\textsc{Keccak}}
\newcommand{\shaThree}{\texttt{SHA-3}}
\newcommand{\nist}{\texttt{NIST}}
\newcommand{\fips}{\texttt{FIPS 202}}
\newcommand{\saw}{\texttt{SAW}}
\newcommand{\sawcore}{SAWCore}
\newcommand{\cryptol}{Cryptol}
\newcommand{\openssl}{OpenSSL}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\algoref}[1]{Alg.~\ref{#1}}
\newcommand{\lineref}[1]{Line~\ref{#1}}
\newcommand{\secref}[1]{Sec.~\ref{#1}}

\begin{document}
%
\title{Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
  Parker Hanson\inst{1} \and
  Benjamin Winters\inst{1} \and
  Eric Mercer\inst{1}\orcidID{0000-0002-2264-2958} \and
  Brett Decker\inst{1}
}
%
\authorrunning{P. Hanson et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
  Brigham Young University, Provo UT 84602, USA
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{abstract}
\keywords{verification \and cryptography \and symbolic execution \and SHA3.}
\end{abstract}

@@

\section{\fips\ Specification in \cryptol}\label{sec:fips}
\input{fips202}

\section{\openssl\ Differences}\label{sec:openssl}
\input{openssl}
